D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-25 ootavacuous.tex
Improve mention of fused loads for non-volatiles
Section 8.2 has a section about fusing loads of non-volatile atomic
objects.  Make it clear that this applies even to quasi-volatile
objects, as mentioned in section 5.4.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

This provides an example of the ``one-to-one'' bullet of
Section~\ref{sec:Volatile and Quasi Volatile Accesses}.

>>>>

This holds even when the atomic objects are quasi volatile,
providing an example of how the ``one-to-one'' bullet of
Section~\ref{sec:Volatile and Quasi Volatile Accesses} does not apply
to them.
